Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-07-15 MSc-dissertation.tex
New para

@@

@@

\subsection{Implementations on models}

@@

@@

>>>>

As the key focus of this project is on the parameter estimations of dynamical system, the ability of inference on the proposed model is firstly examined before actual inference using the experimental observed data.

In the first part, synthetic data is used with known true parameter values. The algorithm implementation is evaluated by the efficiency and goodness of resultant model under different implementation options and ABC SMC hyperparameters.

Then according to findings in the first part, several options with good performance are tried in the inference using experimental observed data (Figure \ref{fig:obs_data}). To obtain a more accurate and general results, these experiments are repeated for 3 or more times.

@@

The ABC SMC inference can have largely different performance when using different hyperparameters and implementation options. Among them the following is studied using synthetic data:

\paragraph{Perturbation kernels}

Perturbation kernels work in the sampling process. In each generation $t$, samples are firstly taken from the previous population $\{\theta_{t-1}\}$ with weights $\{w_{t-1}\}$, then perturbed using the perturbation kernel $K(\theta|\theta^*)$. We keep sampling until $N$ particles are accepted, where $N$ is the pre-set population size. After that the new weights are calculated and normalised.

\begin{figure}
    \begin{center}
    \resizebox{1.0\hsize}{!}{\includegraphics{fig/smc.png}}
    \end{center}

    \caption{ABC SMC sampling process} 
    \label{fig:smc}

The perturbation kernel is called in the sampling of every particles and determines how the new perturbed particle is chosen, thus it is influential to both computation complexity and the resultant posterior distribution. Generally, a local perturbation kernel may face the risk of being stuck in local modes (e,g., local optimal), but it may need less computational operations, or could generate a population with a higher acceptance rate if the successive epsilon values are close; A kernel with wide variance, or spreading out in a large space could help in resolving the local optimal problem by a more thoroughly exploration of the parameter space, however it can be more computation-intensive and result in a lower acceptance rate. A desired optimal kernel should balance the trade-offs; their property and criteria is discussed in \cite{ref:kernel}.

There are several common choice of perturbation kernels. Among them multivariate normal kernel and local M-nearest neighbour model is preferred to be applied on our models.

@@

\subsection{Implementations and code}

@@

[how the code is developed and built]

@@

\bibitem{ref:kernel} Filippi, S., Barnes, C. P., Cornebise, J., and Stumpf, M..H. (2013). On optimality of kernels for approximate Bayesian computation using sequential Monte Carlo. Statistical Applications in Genetics and Molecular Biology 12, 1, 87-107
